Empirical normative theories

### 2020-08-04 simple.tex
Somewhat simpler procedure presentation

Second, the concept of nudge \citep{thaler_nudge:_2009} has been tremendously popular in the recent past, but has also been vastly criticized: the risk of manipulation is particularly high whenever it is unsure that the individual would indeed have adopted the decision that the nudge suggests after careful thinking.

@@

Given a normative theory and two empirical theories for that normative theory and $i \in I$, 
a \emph{test procedure with $i$} is a finite sequence $({\hist}^k)_{k \in \intvl{1, N}}$, for some $N \in \N^*$, of sequences of arguments, 
such that $\forall k \in \intvl{2, N}, {\hist}^k$ starts with ${\hist}^{k-1}$, and 
such that $(i, \phi, {\hist}^N)$ falsifies one of the empirical theories for some $\phi \in \Phi$. 
A sequence of arguments $\histp$ starts with a sequence of arguments $\hist$ of length $l$ iff $\histp$ has length at least $l$ and $\forall k \in \intvl{1, l}: \histp_k = \hist_k$.
\commentOC{Need the test procedure to be a tree. Atom: $(k, \phi)$ meaning whether ${\hist}^k \ileadstost \phi$. Branch label: atoms linked using or and and operators. From a node $n = (\hist, \ar, \phi)$, let branches depart, such that their labels do not overlap. From a node, if no branch label is true, the node must falsify a theory. In the case of the procedure below, it is not a list because we may query several times the same theory or switch to the other one, depending on the last answer. But if simplifying the theory (single-try), we may then simplify the definition of a test procedure.}

\begin{theorem}
	Given two incompatible empirical theories for a given normative theory, $\alpha = (\gleadsto[\alpha], \gbeats[\alpha], \alldargs, \dbeats[\alpha], +_\alpha)$ and $\beta = (\gleadsto[\beta], \gbeats[\beta], \alldargs, \dbeats[\beta], +')$ and given any $i \in I$, there exists a test procedure with $i$ that falsifies one of these theories.
\end{theorem}
\begin{proof}
	Pick any $\phi \in \Phi$ about which $\alpha$ and $\beta$ disagree.

@@

	Given that $\exists K_\alpha \suchthat (\dfp[\alpha])^{K_\alpha}(\gleadstoinv[\alpha](\phi)) = \emptyset$ and $K_\beta \suchthat (\dfp[\beta])^{K_\beta}(\gleadstoinv[\beta](¬\phi)) = \emptyset$ by definition of empirical theories, this process must end with a falsifying instance of $\alpha$ or $\beta$.
\end{proof}

>>>>

Second, the concept of nudge \citep{thaler_nudge:_2009} has been tremendously popular in the recent past, but has also been vastly criticized: the risk of manipulation is particularly high whenever it is unsure that the individual would indeed, after careful thinking, have adopted the decision that the nudge promotes.

@@

%Given a normative theory and two empirical theories for that normative theory and $i \in I$, 
%a \emph{test procedure with $i$} is a finite sequence 
\commentOC{Need the test procedure to be a tree. Atom: $(k, \phi)$ meaning whether ${\hist}^k \ileadstost \phi$. Branch label: atoms linked using or and and operators. From a node $n = (\hist, \ar, \phi)$, let branches depart, such that their labels do not overlap. From a node, if no branch label is true, the node must falsify a theory. In the case of the procedure below, it is not a list because we may query several times the same theory or switch to the other one, depending on the last answer. But if simplifying the theory (single-try), we may then simplify the definition of a test procedure.}

An increasing sequence of arguments is a finite sequence $({\hist}^k)_{k \in \intvl{1, N}}$, for some $N \in \N^*$, of sequences of arguments, 
such that $\forall k \in \intvl{2, N}, {\hist}^k$ starts with ${\hist}^{k-1}$, and 
such that $(i, \phi, {\hist}^N)$ falsifies one of the empirical theories for some $\phi \in \Phi$. 
A sequence of arguments $\histp$ starts with a sequence of arguments $\hist$ of length $l$ iff $\histp$ has length at least $l$ and $\forall k \in \intvl{1, l}: \histp_k = \hist_k$.

Given two incompatible empirical theories for a given normative theory, $\alpha = (\gleadsto[\alpha], \gbeats[\alpha], \alldargs_\alpha, \dbeats[\alpha], +_\alpha)$ and $\beta = (\gleadsto[\beta], \gbeats[\beta], \alldargs_\beta, \dbeats[\beta], +_\beta)$ and given any $i \in I$, the following procedure falsifies one of these theories, involve only $i$, and uses queries only about increasing sequences of arguments.
\begin{procedure}
	Pick any $\phi \in \Phi$ about which $\alpha$ and $\beta$ disagree.

@@

	Given that $\exists K_\alpha \suchthat (\dfp[\alpha])^{K_\alpha}(\gleadstoinv[\alpha](\phi)) = \emptyset$ and $K_\beta \suchthat (\dfp[\beta])^{K_\beta}(\gleadstoinv[\beta](¬\phi)) = \emptyset$ by definition of empirical theories, this process must end with a falsifying instance of $\alpha$ or $\beta$.
\end{procedure}
